Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2023-11-14 manuscript/manuscript.Rmd
Work in progress.

```{r decreased-normality, echo=FALSE, fig.cap=cap, fig.height=2.0, warning=FALSE}
cap <- paste0(
  "Power transformations may reduce normality depending on location. ",
  "Variable $x$ consists of $10000$ values randomly drawn from a normal distribution $\\mathcal{N}(\\mu, 1)$. ",
  "For both Box-Cox and Yeo-Johnson transformations, we would expect $\\lambda = 1$, since $x$ is already normally distributed. ",
  "The figure shows that instead, $\\lambda$ is strongly dependent on the location $\\mu$, ",
  "and even breaks down due to numerical issues for $\\mu > 5 \\cdot 10^4$.")

@@

\begin{equation}
\alpha = \sqrt{\frac{2} {\sqrt{2 \beta_2 - 1} - 2}}
\end{equation}
```

@@

```{=latex}
\begin{equation}
Z_s^2 = \frac{2 \left[\log\left(\beta_1 / \alpha + \sqrt{\beta_1^2 / \alpha^2 + 1} \right) \right]^2}{\log\left(\sqrt{2 \beta_2 - 1} - 1 \right)}
\end{equation}
```

@@

```{=latex}
\begin{equation}
Z_k^2 = \frac{9 \alpha_1}{2} \left[ 1 - \frac{2}{9 \alpha_1} - \left(\frac{1 - 2 / \alpha_1}{1 + \alpha_2 \sqrt{2 / \left(\alpha_1 - 4 \right)}} \right)^{1 / 3}  \right]^2
\end{equation}
```

>>>>

```{r decreased-normality, echo=FALSE, fig.cap=cap, fig.height=4.0, warning=FALSE}
cap <- paste0(
  "Power transformations may reduce normality depending on location. ",
  "Variable $x$ consists of $10000$ values randomly drawn from a normal distribution. ",
  "For the top row, that distribution is parameterised as $\\mathcal{N}(\\mu, 1)$, ",
  "whereas for the bottom row, the distribution is $\\mathcal{N}(0, \\sigma)$.",
  "For both Box-Cox and Yeo-Johnson transformations, we would expect $\\lambda = 1$, since $x$ is already normally distributed. ",
  "The figure shows that instead, $\\lambda$ is strongly dependent on the location $\\mu$, ",
  "and breaks down due to numerical issues for $\\mu > 10^3$ (both Box-Cox and Yeo-Johnson) ",
  "and $\\sigma > 10^3 (Yeo-Johnson) only."
)

@@

\begin{equation}
\alpha = \sqrt{\frac{2} {\sqrt{2 \beta_2 - 2} - 2}}
\end{equation}

\begin{equation}
\delta = \frac{1}{\sqrt{\log \left[\sqrt{-1 + \sqrt{2 * \beta_2 - 2}} \right]}}
\end{equation}
```

@@

```{=latex}
\begin{equation}
Z_s = \delta \log\left[\frac{\beta_1}{\alpha} + \sqrt{\frac{\beta_1^2}{\alpha^2} + 1} \right]
\end{equation}
```

@@

```{=latex}
\begin{equation}
Z_k = \sqrt{\frac{9 \alpha_1}{2}} \left[ 1 - \frac{2}{9 \alpha_1} - \left(\frac{1 - 2 / \alpha_1}{1 + \alpha_2 \sqrt{2 / \left(\alpha_1 - 4 \right)}} \right)^{1 / 3}  \right]
\end{equation}
```
